GENEX: Transcript Report

### 2020-05-28 code/02-Transcript_Master.Rmd
Transcript Profilers

Gene <- "GENEX"
#Gene <- "GFAP"

@@

  eval(parse(text=paste0( 'pDat <- data[ data$Comparison == \'', comp,'\' & data$Model == \'', model,'\' & data$ensembl_gene_id %in% Keepers & data$Tissue == \'', tiss ,'\', ]' )))
  pDat$adj.P.Val <- p.adjust( pDat$P.Value, method = 'fdr', n=adj )
  pDat$Direction[pDat$adj.P.Val <= 0.05 & pDat$logFC <= -log2(1.2)] = 'DOWN'
  pDat$Direction[pDat$adj.P.Val <= 0.05 & pDat$logFC >= log2(1.2)] = 'UP'

@@

  if( (tiss %in% c('DLPFC','TCX','PHG')) == T){
    plot <- ggplot(  pDat   , aes(x=logFC, y=ensembl_gene_id , colour=Direction)) +
      scale_y_discrete() + 
      scale_color_manual(values=c("#000000", "#7F0000" , "#000099"), breaks =c("NONE", "UP" , "DOWN")) +
      geom_errorbar(aes(xmin=CI.L, xmax=CI.R), width=.1) +
      geom_line() +
      geom_point() +
      #annotation_custom(grob) 
      ggtitle(paste0(tiss,': ',Gene)) + theme(legend.position = "none") + theme(axis.title.y = element_blank()) +
      theme(axis.text.y = element_text(face="bold", size=6, angle=45)) +
      geom_vline(xintercept = 0, linetype="dotted", color = "black", size=1.5)
  }else{
     plot <- ggplot(  pDat   , aes(x=logFC, y=ensembl_gene_id , colour=Direction)) +
      scale_y_discrete() + 
      scale_color_manual(values=c("#000000", "#7F0000" , "#000099"), breaks =c("NONE", "UP" , "DOWN")) +
      geom_errorbar(aes(xmin=CI.L, xmax=CI.R), width=.1) +
      geom_line() +
      geom_point() +
      #annotation_custom(grob) 
      ggtitle(paste0(tiss,': ',Gene)) + theme(legend.position = "none") + 
      theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
      geom_vline(xintercept = 0, linetype="dotted", color = "black", size=1.5)
  } 
  return(plot)
}

DLPFC <- Log_Plot( Rosmap_DE, 'DLPFC', 'AD-CONTROL', 'Diagnosis.Sex', Rosmap_Adj )
TCX <- Log_Plot( Mayo_DE, 'TCX', 'AD-CONTROL', 'Diagnosis', Mayo_Adj  )
CBE <- Log_Plot( Mayo_DE, 'CBE', 'AD-CONTROL', 'Diagnosis', Mayo_Adj  )
PHG <- Log_Plot( MSBB_DE, 'PHG', 'AD-CONTROL', 'Diagnosis', MSBB_Adj  )
IFG <- Log_Plot( MSBB_DE, 'IFG', 'AD-CONTROL', 'Diagnosis', MSBB_Adj  )
FP <- Log_Plot( MSBB_DE, 'FP', 'AD-CONTROL', 'Diagnosis', MSBB_Adj  )
STG <- Log_Plot( MSBB_DE, 'STG', 'AD-CONTROL', 'Diagnosis', MSBB_Adj  )
```

@@

```{r PlotLog, cache = FALSE, fig.height = 5, fig.width = 14}
grid.arrange(DLPFC, TCX, CBE, PHG, IFG, FP, STG,  ncol=7)
```

@@

  temp <- as.data.frame( EXP[ row.names( EXP )[ row.names( EXP ) %in% Keepers], ] )
  temp$Transcript <- row.names(temp)

@@

  plot <- ggplot(data = foo, aes(x=Var2, y=value)) + 
    geom_violin(  ) + geom_boxplot( width=0.1, outlier.shape = NA) +  theme(legend.position = "none") +
    geom_jitter(aes(col=Diagnosis), alpha = .4, size=.2) + # geom_jitter() +
    theme(axis.text.x = element_text(face="bold", size=6, angle=45)) + ggtitle(paste0(Tiss,': ',Gene)) +
    theme(axis.title.y = element_blank(), axis.title.x = element_blank(), legend.position = "none" )

  return( plot )
}

@@

IFG <- BoxPloter( MSBB_EXP, MSBB_Cov, 'IFG' )
PHG <- BoxPloter( MSBB_EXP, MSBB_Cov, 'PHG' )
FP <- BoxPloter( MSBB_EXP, MSBB_Cov, 'FP' )
STG <- BoxPloter( MSBB_EXP, MSBB_Cov, 'STG' )
```

```{r PlotLog2, cache = FALSE, fig.height = 8, fig.width = 14}
grid.arrange(DLPFC, TCX, CBE, PHG, IFG, FP, STG,ncol=4, nrow=2)
```

>>>>

Gene <- "GENEX"
#Gene <- "CTHRC1"

@@

  eval(parse(text=paste0( 'pDat <- data[ data$Comparison == \'', comp,'\' & data$Model == \'', model,'\' & data$ensembl_gene_id %in% Keepers & data$Tissue == \'', tiss ,'\', ]' )))
  if( dim(pDat)[1] > 0 ){
    pDat$adj.P.Val <- p.adjust( pDat$P.Value, method = 'fdr', n=adj )
    pDat$Direction[pDat$adj.P.Val <= 0.05 & pDat$logFC <= -log2(1.2)] = 'DOWN'
    pDat$Direction[pDat$adj.P.Val <= 0.05 & pDat$logFC >= log2(1.2)] = 'UP'

@@

    if( (tiss %in% c('DLPFC','TCX','PHG')) == T){
      plot <- ggplot(  pDat   , aes(x=logFC, y=ensembl_gene_id , colour=Direction)) +
        scale_y_discrete() + 
        scale_color_manual(values=c("#000000", "#7F0000" , "#000099"), breaks =c("NONE", "UP" , "DOWN")) +
        geom_errorbar(aes(xmin=CI.L, xmax=CI.R), width=.1) +
        geom_line() +
        geom_point() +
        #annotation_custom(grob) 
        ggtitle(paste0(tiss,': ',Gene)) + theme(legend.position = "none") + theme(axis.title.y = element_blank()) +
        theme(axis.text.y = element_text(face="bold", size=6, angle=45)) +
        geom_vline(xintercept = 0, linetype="dotted", color = "black", size=1.5)
    }else{
       plot <- ggplot(  pDat   , aes(x=logFC, y=ensembl_gene_id , colour=Direction)) +
        scale_y_discrete() + 
        scale_color_manual(values=c("#000000", "#7F0000" , "#000099"), breaks =c("NONE", "UP" , "DOWN")) +
        geom_errorbar(aes(xmin=CI.L, xmax=CI.R), width=.1) +
        geom_line() +
        geom_point() +
        #annotation_custom(grob) 
        ggtitle(paste0(tiss,': ',Gene)) + theme(legend.position = "none") + 
        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
        geom_vline(xintercept = 0, linetype="dotted", color = "black", size=1.5)

    } 
  }else{
    plot <- NULL
  }
  return(plot)
}

DLPFC <- Log_Plot( Rosmap_DE, 'DLPFC', 'AD-CONTROL', 'Diagnosis.Sex', Rosmap_Adj )
TCX <- Log_Plot( Mayo_DE, 'TCX', 'AD-CONTROL', 'Diagnosis', Mayo_Adj  )
CBE <- Log_Plot( Mayo_DE, 'CBE', 'AD-CONTROL', 'Diagnosis', Mayo_Adj  )
PHG <- Log_Plot( MSBB_DE, 'PHG', 'AD-CONTROL', 'Diagnosis', MSBB_Adj  )
IFG <- Log_Plot( MSBB_DE, 'IFG', 'AD-CONTROL', 'Diagnosis', MSBB_Adj  )
FP <- Log_Plot( MSBB_DE, 'FP', 'AD-CONTROL', 'Diagnosis', MSBB_Adj  )
STG <- Log_Plot( MSBB_DE, 'STG', 'AD-CONTROL', 'Diagnosis', MSBB_Adj  )

LIST <- NULL
for( test in c('DLPFC','TCX','CBE','PHG','IFG','FP','STG') ){
  if( eval(parse(text= paste0( 'is.null(', test, ')' ))) == TRUE ){
  }else{
    LIST <- c(LIST, test)
  }
}
```

@@

```{r PlotLog, cache = FALSE, fig.height = 5, fig.width = 14}
N<-length(LIST) 
if(length(LIST) == 0 ){

}else{
  PLOTS <- paste0(LIST, collapse=',')
  eval(parse(text= paste0( 'grid.arrange(', PLOTS , ', ncol=', N, ' )' )))
}
```

@@

  temp <- as.data.frame( EXP[ row.names( EXP )[ row.names( EXP ) %in% Keepers], ] )
  if( dim(temp)[1] == 0 ){
    plot <- NULL
  }else{
    temp$Transcript <- row.names(temp)

@@

    plot <- ggplot(data = foo, aes(x=Var2, y=value)) + 
      geom_violin(  ) + geom_boxplot( width=0.1, outlier.shape = NA) +  theme(legend.position = "none") +
      geom_jitter(aes(col=Diagnosis), alpha = .4, size=.2) + # geom_jitter() +
      theme(axis.text.x = element_text(face="bold", size=6, angle=45)) + ggtitle(paste0(Tiss,': ',Gene)) +
      theme(axis.title.y = element_blank(), axis.title.x = element_blank(), legend.position = "none" )
  }
  return( plot )
}

@@

IFG <- BoxPloter( MSBB_EXP, MSBB_Cov, 'IFG' )
PHG <- BoxPloter( MSBB_EXP, MSBB_Cov, 'PHG' )
FP <- BoxPloter( MSBB_EXP, MSBB_Cov, 'FP' )
STG <- BoxPloter( MSBB_EXP, MSBB_Cov, 'STG' )

LIST <- NULL
for( test in c('DLPFC','TCX','CBE','PHG','IFG','FP','STG') ){
  if( eval(parse(text= paste0( 'is.null(', test, ')' ))) == TRUE ){
  }else{
    LIST <- c(LIST, test)
  }
}

```

```{r PlotLog2, cache = FALSE, fig.height = 8, fig.width = 14}
N<-length(LIST) 
if(length(LIST) == 0 ){

}else{
  if(length(LIST) > 4 ){
    PLOTS <- paste0(LIST, collapse=',')
    eval(parse(text= paste0( 'grid.arrange(', PLOTS , ', ncol=4, nrow=2 )' )))
  }else{
    PLOTS <- paste0(LIST, collapse=',')
    eval(parse(text= paste0( 'grid.arrange(', PLOTS , ', ncol=4, nrow=1 )' )))
  }
}

#grid.arrange(DLPFC, TCX, CBE, PHG, IFG, FP, STG,ncol=4, nrow=2)
```
